Appendix A: Simulation Details and Results

### 2014-11-14 supp/sim_tables_appendix.tex
Removed comments
Switched landscape to sideways in appendix
Finishing new reviewer comments, moved tables and figures around

\documentclass{article}
\usepackage[letterpaper,hmargin={2.4cm,2.4cm},vmargin={2.4cm,2.4cm}]{geometry}
\usepackage[pdftex,hidelinks]{hyperref}
\usepackage{soul}
\usepackage{graphicx}
\usepackage{amsmath}
%\usepackage{rotating}
\usepackage{pdflscape}

\begin{document}
\title{Appendix A: Simulation Details and Results}
\date{} %remove date
\maketitle
\renewcommand*\thetable{A\arabic{table}}
\renewcommand*\thefigure{A\arabic{figure}}
\renewcommand*\theequation{A\arabic{equation}}

@@

%\section*{Simulation Setup and Results Tables}
\begin{table}[t]
  \centering
\caption{Changed parameter values, by series of simulations.  We
simulated 1000 sets of data each combination of parameter values
for 100 sites over 40 years.  We assumed that initial abundance
($\Lambda$) was Poisson distributed.  For the exponential 
simulations we included all combinations of low, medium, and
high $\Lambda$, growth rate ($r$), and detection probability ($p$).
For the Ricker model simulations we used $\Lambda$ = 10 and $p$ = 0.25, and
simulated low, medium, and high values of $r$ and equilibrium density ($K$).
For the Ricker + immigration dynamics model we fixed all parameters the
same as the Ricker model (with $r$ = 0.05 and $K$ = 10) and
simulated low, medium, and high values of immigration rate ($\iota$).}  
\begin{tabular}{lcccccccc}
    \hline
    & \multicolumn{3}{c}{Exponential Growth} && \multicolumn{2}{c}{Ricker} &&
    Ricker + Immigration \\
    \cline{2-4}     \cline{6-7}    \cline{9-9}
& $\Lambda$ & $r$ & $p$ && $r$  & $K$ && $\iota$  \\    
\hline
    Low	        &1	&-0.01	&0.05	&&0.005	 &5	&&0.005  \\
    Med	        &5	&0	&0.25	&&0.05	&10	&&0.05   \\
    High		 &10 &0.005	&0.5	&&0.1	&20	&&0.5    \\
    \hline
  \end{tabular}
\end{table}

%\clearpage

\begin{landscape}

\begin{table}[htb]
  \centering
  \footnotesize
  \caption{Simulation results from 27 cases of exponential dynamics with 1000 Monte Carlo replicates for each.}
  \begin{tabular}{cccccccccccc}
    \hline
    \multicolumn{3}{c}{Data generating values}&
    \multicolumn{3}{c}{Mean} &
    \multicolumn{3}{c}{RMSE} &
    \multicolumn{3}{c}{Coverage} \\
    \multicolumn{3}{c}{\rule{4cm}{1pt}} &
    \multicolumn{3}{c}{\rule{4cm}{1pt}} &
    \multicolumn{3}{c}{\rule{4cm}{1pt}} &
    \multicolumn{3}{c}{\rule{4cm}{1pt}} \\
%    \hline
    $\Lambda$ & $r$ & $p$ & $\Lambda$ & $r$ & $p$ & $\Lambda$ & $r$ &
    $p$ & $\Lambda$ & $r$ & $p$ \\
    \hline
10	&-0.005	&0.05	&10.03924	&-0.00601	&0.05007	&1.05051	&0.00605	&0.00432	&0.959	&0.945	&0.96\\
10	&-0.005	&0.25	&10.0333	&-0.00573	&0.25&0.76926	&0.00598	&0.01545 &0.951	&0.942	&0.945\\
10	&-0.005	&0.5	&10.00858	&-0.00598	&0.49984	&0.61057	&0.00532	&0.02352	&0.949	&0.957	&0.945\\
10	&0.005	&0.05	&10.06802	&0.00424	&0.04996	&1.04574	&0.00576	&0.00428	&0.955	&0.939	&0.949\\
10	&0.005	&0.25	&10.03648	&0.00399	&0.25087	&0.80109	&0.00525	&0.01665	&0.934	&0.954	&0.921\\
10	&0.005	&0.5	&9.96719	&0.00431	&0.50244	&0.61777	&0.00492	&0.02539	&0.934	&0.957	&0.92\\
10	&0	&0.05	&10.06548	&-9e-04	        &0.05001	&1.06134	&0.00553	&0.0046	&0.961	&0.96	&0.944\\
10	&0	&0.25	&10.03522	&-0.00093	&0.25012	&0.76321	&0.00555	&0.01585	&0.953	&0.943	&0.936\\
10	&0	&0.5	&10.0036	&-0.00067	&0.50052	&0.58102	&0.00544	&0.02274	&0.949	&0.945	&0.948\\
1	&-0.005	&0.05	&1.04714	&-0.01254	&0.05045	&0.24087	&0.02411	&0.00915	&0.949	&0.953	&0.97\\
1	&-0.005	&0.25	&1.01614	&-0.01173	&0.25038	&0.15418	&0.02267	&0.02749	&0.952	&0.949	&0.945\\
1	&-0.005	&0.5	&1.01056	&-0.01136	&0.50008	&0.13529	&0.02287	&0.03846	&0.957	&0.936	&0.95\\
1	&0.005	&0.05	&1.0281	        &-5e-05	        &0.05032	&0.23616	&0.02057	&0.00954	&0.939	&0.948	&0.947\\
1	&0.005	&0.25	&1.01389	&-0.00143	&0.2502	&0.1609	&0.02246	&0.0268	&0.957	&0.937	&0.946\\
1	&0.005	&0.5	&1.00554	&-0.00114	&0.50194	&0.13693	&0.02064	&0.03746	&0.947	&0.945	&0.95\\
1	&0	&0.05	&1.03641	&-0.00685	&0.05017	&0.23656	&0.02457	&0.00928	&0.958	&0.934	&0.961\\
1	&0	&0.25	&1.01556	&-0.00587	&0.24993	&0.16434	&0.02134	&0.02592	&0.944	&0.945	&0.953\\
1	&0	&0.5	&1.00539	&-0.00533	&0.49994	&0.13367	&0.01982	&0.03812	&0.951	&0.947	&0.952\\
5	&-0.005	&0.05	&5.07525	&-0.00638	&0.04978	&0.65646	&0.00881	&0.00496	&0.945	&0.959	&0.965\\
5	&-0.005	&0.25	&5.02641	&-0.00619	&0.25013	&0.4727	&0.00779	&0.01735	&0.943	&0.966	&0.937\\
5	&-0.005	&0.5	&5.01265	&-0.00656	&0.50067	&0.36154	&0.00814	&0.02465	&0.96	&0.949	&0.961\\
5	&0.005	&0.05	&5.05623	&0.00396	&0.05002	&0.62418	&0.00786	&0.00505	&0.944	&0.957	&0.952\\
5	&0.005	&0.25	&5.01567	&0.0041	&0.25014	&0.44585	&0.00746	&0.01723	&0.948	&0.947	&0.942\\
5	&0.005	&0.5	&5.02672	&0.00368	&0.49908	&0.36657	&0.00727	&0.02475	&0.947	&0.95	&0.943\\
5	&0	&0.05	&5.06304	&-0.00162	&0.04994	&0.61073	&0.00838	&0.00492	&0.96	&0.96	&0.956\\
5	&0	&0.25	&5.04372	&-0.00141	&0.24927	&0.46542	&0.00812	&0.01709	&0.942	&0.938	&0.945\\
5	&0	&0.5	&5.0239	&-0.00117	&0.4991	&0.37326	&0.00747	&0.02487	&0.952	&0.964	&0.946\\
  \hline
  \end{tabular}
  \label{tab:simexp}
\end{table}
\clearpage

\begin{table}
  \centering
  \footnotesize
  \caption{Simulation results from 9 cases of Ricker dynamics with 1000 Monte Carlo replicates for each.}
  \begin{tabular}{cccccccccccccccc}
    \hline
    \multicolumn{4}{c}{Data generating values}&
    \multicolumn{4}{c}{Mean} &
    \multicolumn{4}{c}{RMSE} &
    \multicolumn{4}{c}{Coverage} \\
    \multicolumn{4}{c}{\rule{4cm}{1pt}} &
    \multicolumn{4}{c}{\rule{4cm}{1pt}} &
    \multicolumn{4}{c}{\rule{4cm}{1pt}} &
    \multicolumn{4}{c}{\rule{4cm}{1pt}} \\
%    \hline
    $\Lambda$ & $r$ & $K$ & $p$ & $\Lambda$ & $r$ & $K$ & $p$ & $\Lambda$ & $r$ & $K$ &
    $p$ & $\Lambda$ & $r$ & $K$ & $p$ \\
    \hline
10	&0.005	&5	&0.25	&9.914 &0.00982  &6.368 &0.25211	&0.78540 &0.01147   &5.56126 &0.01614	&0.955 &0.807 &0.776 &0.963\\
10	&0.005	&10	&0.25	&9.954 &0.00866 &10.989 &0.25179 &0.77529 &0.00929   &8.73913 &0.01613  &0.960 &0.831 &0.828 &0.943\\
10	&0.005	&20	&0.25	&9.935 &0.00827 &59.778 &0.25145 &0.76079 &0.00830 &418.37837 &0.01559  &0.955 &0.841 &0.943 &0.955\\
10	&0.05	&5	&0.25	&10.038 &0.05290  &4.682 &0.25160 &0.89588 &0.02748   &1.58258 &0.01884  &0.945 &0.922 &0.919 &0.951\\
10	&0.05	&10	&0.25	&10.009 &0.05270  &9.718 &0.25172 &0.83411 &0.01876   &1.74552 &0.01742  &0.961 &0.930 &0.960 &0.948\\
10	&0.05	&20	&0.25	&10.000 &0.05136 &19.790 &0.25082 &0.83906 &0.01316   &2.51289 &0.01670  &0.951 &0.943 &0.962 &0.940\\
10	&0.1	&5	&0.25	&10.046 &0.10127  &4.833 &0.25048 &0.91333 &0.03529   &0.87551 &0.01953  &0.948 &0.954 &0.944 &0.954\\
10	&0.1	&10	&0.25	&9.990 &0.10254  &9.893 &0.25143 &0.88385 &0.02267   &0.89598 &0.01800  &0.949 &0.954 &0.964 &0.950\\
10	&0.1	&20	&0.25	&9.988 &0.10185 &19.916 &0.25117 &0.85780 &0.01543   &1.62111 &0.01680  &0.947 &0.941 &0.951 &0.953\\
  \hline
  \end{tabular}
  \label{tab:simricker}
\end{table}

\clearpage
\begin{table}
  \centering
  \footnotesize
  \caption{Simulation results from 3 cases of Ricker and immigration dynamics with 1000 Monte Carlo replicates for each.}
  \begin{tabular}{cccccccccccccccccccc}
    \hline
    \multicolumn{5}{c}{Data generating values}&
    \multicolumn{5}{c}{Mean} &
    \multicolumn{5}{c}{RMSE} &
    \multicolumn{5}{c}{Coverage} \\
    \multicolumn{5}{c}{\rule{4cm}{1pt}} &
    \multicolumn{5}{c}{\rule{7cm}{1pt}} &
    \multicolumn{5}{c}{\rule{7cm}{1pt}} &
    \multicolumn{5}{c}{\rule{4cm}{1pt}} \\
%    \hline
    $\Lambda$ & $r$ & $K$ & $\iota$ & $p$ & $\Lambda$ & $r$ & $K$ & $\iota$ & $p$ & $\Lambda$ & $r$ & $K$ &
    $\iota$ & $p$ & $\Lambda$ & $r$ & $K$ & $\iota$ & $p$ \\
    \hline
10 &0.05 &10 &0.005 &0.25  &9.997 &0.05148 &9.687 &0.00510 &0.25077 &0.87742 &0.01805 &1.77679 &0.00315 &0.01795  &0.951 &0.944 &0.964 &0.947 &0.942\\
10 &0.05 &10 &0.050 &0.25 &10.015 &0.05166 &9.758 &0.05039 &0.25070 &0.87490 &0.01731 &1.72376 &0.01055 &0.01839  &0.943 &0.932 &0.958 &0.940 &0.943\\
10 &0.05 &10 &0.500 &0.25 &10.000 &0.05057 &9.648 &0.50811 &0.25110 &0.96491 &0.01942 &2.68264 &0.07763 &0.02050  &0.947 &0.940 &0.952 &0.951 &0.941\\
  \hline
  \end{tabular}
  \label{tab:simricki}
\end{table}
\clearpage

\begin{table}[htb]
  \centering
  \footnotesize
  \caption{Parameters of geometric-recruitment simulation (1000 Monte Carlo replicates)
  and results of exponential and geometric-recruitment models fit to these data.}
  \begin{tabular}{lccccccccccccccccc}
    \hline
    & \multicolumn{5}{c}{Mean} &&
    \multicolumn{5}{c}{RMSE} &&
    \multicolumn{5}{c}{Coverage} \\
    \cline{2-6}     \cline{8-12}    \cline{14-18}
    Model & $\Lambda$ & $\gamma$ & $\omega$ & $r$\footnotemark[1] & $p$ &&
    $\Lambda$ & $\gamma$ & $\omega$ & $r$ & $p$ && 
    $\Lambda$ & $\gamma$ & $\omega$ & $r$ & $p$ \\
    \hline
Simulation & 
10	&0.5	&0.5	&0	&0.25	&&-	&-	&-	&-	&-	&&-	&-	&-	&-	&-\\
Exponential &
12.710	&-	&- 	&-0.00052 	&0.19728	&&
2.8808	&-	&- 	&0.00458	&0.05424	&&
0.130	&-	&- 	&0.957 	&0.039 \\
Geometric-recruitment &
10.457	&0.57321	&0.42621	&- 	&0.24269	&&
1.39877 &0.17905	&0.17944	&- 	&0.02925	&&
0.851	&0.935	&0.932	&- 	&0.814 \\
  \hline
  \multicolumn{18}{c}{$^{1}$ Derived parameter: $r = \log(\gamma + \omega)$.}
  \end{tabular}
  \label{tab:simgeom}
\end{table}

@@

\begin{table}[htb]
  \centering
  \footnotesize
  \caption{Results of exponential and geometric-recruitment models fit to Leslie matrix simulation (1000 Monte Carlo replicates).}
  \begin{tabular}{lccccccccccccc}
    \hline
    & \multicolumn{5}{c}{Mean} &&
    \multicolumn{3}{c}{RMSE} &&
    \multicolumn{3}{c}{Coverage} \\
    \cline{2-6}     \cline{8-10}    \cline{12-14}
    Model & $\Lambda$ & $\gamma$ & $\omega$ & $r$\footnotemark[1] & $p$ &&
    $\Lambda$ & $r$ & $p$ && 
    $\Lambda$ & $r$ & $p$ \\
    \hline
Exponential &
27.841	&-	&- 	&-0.00470	&0.09037	&&
17.97942	&0.00186 	&0.15979	&&
0.000 		&0.977 	&0.000 \\
Geometric-recruitment &
12.782	&0.21211	&0.78326	&-	&0.19720	&&
2.92896 	&- 	&0.05438	&&
0.057		&- 	&0.022 \\
  \hline
  \multicolumn{14}{c}{$^{1}$ Derived parameter: $r = \log(\gamma + \omega)$.}
  \end{tabular}
  \label{tab:simmat}
\end{table}
\clearpage

\begin{table}[htb]
  \centering
  \footnotesize
  \caption{Parameters of Gompertz simulation with two generation per year 
(1000 Monte Carlo replicates)
  and results of models fit to these data.}
  \begin{tabular}{lcccccccccccccc}
    \hline
    & \multicolumn{4}{c}{Mean} &&
    \multicolumn{4}{c}{RMSE} &&
    \multicolumn{4}{c}{Coverage} \\
    \cline{2-5}     \cline{7-10}    \cline{12-15}
    Model & $\Lambda$ & $r$ & $K$ & $p$ &&
    $\Lambda$ & $r$ & $K$ & $p$ && 
    $\Lambda$ & $r$ & $K$ & $p$ \\
    \hline
Simulation & 
10	&0.05	&10	&0.5	&&-	&-	&-	&-	&&-	&-	&-	&-\\
Gompertz (MLE; 1 generation/year) &
8.392	&0.00919	&1.269	&0.60241	&&
1.64842	&-	&8.94192	&0.10395	&&
0.013	&-	&1.000 	&0.000 \\
Gompertz (MCMC; 1 generation/year) &
8.315	&0.03044	&4.575	&0.60723	&&
1.72224	&-	&5.70813	&0.10870	&&
0.007	&-	&0.368		&0.000 \\
Gompertz (MCMC; 2 generations/year) &
9.969	&0.05405	&10.407	&0.50337	&&
0.55084	&0.01697	&2.26087	&0.02318	&&
0.921	&0.964	&0.967	&0.935 \\
  \hline
  \end{tabular}
  \label{tab:simgomp}
\end{table}

@@

\begin{figure}
\caption{Histograms of 1000 parameter estimates for each of nine
simulation cases with Ricker dynamics. The blue vertical lines are the 
data-generating values.}
  \centering
  \includegraphics{../figs/rick_hists}
\label{fig:rick_hists}
\end{figure}

\begin{figure}
\caption{Histograms of 1000 parameter estimates for each of three
simulation cases with Ricker + immigration dynamics. The blue vertical lines are the 
data-generating values.}
  \centering
  \includegraphics[width=8.5in]{../figs/ricki_hists}
\label{fig:ricki_hists}
\end{figure}

\begin{figure}
\caption{Histograms of 1000 parameter estimates for each of two
simulation cases with geometric-recruitment or Leslie matrix dynamics, each fit with 
exponential and geometric-recruitment models. The blue vertical lines are the 
data-generating values; the data-generating values for $r$ are derived from
the actual dynamic parameters of these models.  No data-generating values
are provided for $\gamma$ or $\omega$ by the Leslie matrix model because
each age class had its own survival and fecundity parameters.}
  \centering
  \includegraphics{../figs/geom_mat_hists}
\label{fig:geom_mat_hists}
\end{figure}

\begin{figure}
\caption{Histograms of 1000 parameter estimates simulated with Gompertz dynamics, 
two generations per year, fit with three different Gompertz models.
The vertical lines are the data-generating values; changing the number of generations
changes the meaning of $r$, so no data-generating values of it are provided for the 
single generation per year cases.}
  \centering
  \includegraphics{../figs/gomp_hists}
\label{fig:gomp_hists}
\end{figure}
\end{landscape}

>>>>

\documentclass{article}
\usepackage[letterpaper,hmargin={2.4cm,2.4cm},vmargin={2.4cm,2.4cm}]{geometry}
\usepackage[pdftex,hidelinks]{hyperref}
\usepackage{soul}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{rotating}
\usepackage{pdflscape}

\begin{document}
\title{Appendix A: Simulation Details and Results}
\date{} 
\maketitle
\renewcommand*\thetable{A\arabic{table}}
\renewcommand*\thefigure{A\arabic{figure}}
\renewcommand*\theequation{A\arabic{equation}}

@@

\begin{table}[t]
  \centering
\caption{Changed parameter values, by series of simulations.  We
simulated 1000 sets of data each combination of parameter values
for 100 sites over 40 years.  We assumed that initial abundance
($\Lambda$) was Poisson distributed.  For the exponential 
simulations we included all combinations of low, medium, and
high $\Lambda$, growth rate ($r$), and detection probability ($p$).
For the Ricker model simulations we used $\Lambda$ = 10 and $p$ = 0.25, and
simulated low, medium, and high values of $r$ and equilibrium density ($K$).
For the Ricker + immigration dynamics model we fixed all parameters the
same as the Ricker model (with $r$ = 0.05 and $K$ = 10) and
simulated low, medium, and high values of immigration rate ($\iota$).}  
\begin{tabular}{lcccccccc}
    \hline
    & \multicolumn{3}{c}{Exponential Growth} && \multicolumn{2}{c}{Ricker} &&
    Ricker + Immigration \\
    \cline{2-4}     \cline{6-7}    \cline{9-9}
& $\Lambda$ & $r$ & $p$ && $r$  & $K$ && $\iota$  \\    
\hline
    Low	        &1	&-0.01	&0.05	&&0.005	 &5	&&0.005  \\
    Med	        &5	&0	&0.25	&&0.05	&10	&&0.05   \\
    High		 &10 &0.005	&0.5	&&0.1	&20	&&0.5    \\
    \hline
  \end{tabular}
\end{table}

%\begin{landscape}

\begin{sidewaystable}[htb]
  \centering
  \footnotesize
  \caption{Parameters of geometric-recruitment simulation (1000 Monte Carlo replicates)
  and results of exponential and geometric-recruitment models fit to these data.}
  \begin{tabular}{lccccccccccccccccc}
    \hline
    & \multicolumn{5}{c}{Mean} &&
    \multicolumn{5}{c}{RMSE} &&
    \multicolumn{5}{c}{Coverage} \\
    \cline{2-6}     \cline{8-12}    \cline{14-18}
    Model & $\Lambda$ & $\gamma$ & $\omega$ & $r$\footnotemark[1] & $p$ &&
    $\Lambda$ & $\gamma$ & $\omega$ & $r$ & $p$ && 
    $\Lambda$ & $\gamma$ & $\omega$ & $r$ & $p$ \\
    \hline
Simulation & 
10	&0.5	&0.5	&0	&0.25	&&-	&-	&-	&-	&-	&&-	&-	&-	&-	&-\\
Exponential &
12.710	&-	&- 	&-0.00052 	&0.19728	&&
2.8808	&-	&- 	&0.00458	&0.05424	&&
0.130	&-	&- 	&0.957 	&0.039 \\
Geometric-recruitment &
10.457	&0.57321	&0.42621	&- 	&0.24269	&&
1.39877 &0.17905	&0.17944	&- 	&0.02925	&&
0.851	&0.935	&0.932	&- 	&0.814 \\
  \hline
  \multicolumn{18}{c}{$^{1}$ Derived parameter: $r = \log(\gamma + \omega)$.}
  \end{tabular}
  \label{tab:simgeom}
\end{sidewaystable}

@@

\begin{sidewaystable}[htb]
  \centering
  \footnotesize
  \caption{Results of exponential and geometric-recruitment models fit to Leslie matrix simulation (1000 Monte Carlo replicates).}
  \begin{tabular}{lccccccccccccc}
    \hline
    & \multicolumn{5}{c}{Mean} &&
    \multicolumn{3}{c}{RMSE} &&
    \multicolumn{3}{c}{Coverage} \\
    \cline{2-6}     \cline{8-10}    \cline{12-14}
    Model & $\Lambda$ & $\gamma$ & $\omega$ & $r$\footnotemark[1] & $p$ &&
    $\Lambda$ & $r$ & $p$ && 
    $\Lambda$ & $r$ & $p$ \\
    \hline
Exponential &
27.841	&-	&- 	&-0.00470	&0.09037	&&
17.97942	&0.00186 	&0.15979	&&
0.000 		&0.977 	&0.000 \\
Geometric-recruitment &
12.782	&0.21211	&0.78326	&-	&0.19720	&&
2.92896 	&- 	&0.05438	&&
0.057		&- 	&0.022 \\
  \hline
  \multicolumn{14}{c}{$^{1}$ Derived parameter: $r = \log(\gamma + \omega)$.}
  \end{tabular}
  \label{tab:simmat}
\end{sidewaystable}
\clearpage

\begin{sidewaystable}[htb]
  \centering
  \footnotesize
  \caption{Parameters of Gompertz simulation with two generation per year 
(1000 Monte Carlo replicates)
  and results of models fit to these data.}
  \begin{tabular}{lcccccccccccccc}
    \hline
    & \multicolumn{4}{c}{Mean} &&
    \multicolumn{4}{c}{RMSE} &&
    \multicolumn{4}{c}{Coverage} \\
    \cline{2-5}     \cline{7-10}    \cline{12-15}
    Model & $\Lambda$ & $r$ & $K$ & $p$ &&
    $\Lambda$ & $r$ & $K$ & $p$ && 
    $\Lambda$ & $r$ & $K$ & $p$ \\
    \hline
Simulation & 
10	&0.05	&10	&0.5	&&-	&-	&-	&-	&&-	&-	&-	&-\\
Gompertz (MLE; 1 generation/year) &
8.392	&0.00919	&1.269	&0.60241	&&
1.64842	&-	&8.94192	&0.10395	&&
0.013	&-	&1.000 	&0.000 \\
Gompertz (MCMC; 1 generation/year) &
8.315	&0.03044	&4.575	&0.60723	&&
1.72224	&-	&5.70813	&0.10870	&&
0.007	&-	&0.368		&0.000 \\
Gompertz (MCMC; 2 generations/year) &
9.969	&0.05405	&10.407	&0.50337	&&
0.55084	&0.01697	&2.26087	&0.02318	&&
0.921	&0.964	&0.967	&0.935 \\
  \hline
  \end{tabular}
  \label{tab:simgomp}
\end{sidewaystable}

@@

\begin{figure}
\caption{Histograms of 1000 parameter estimates for each of 27
simulation cases with exponential dynamics. The vertical lines are the 
data-generating values.}
  \centering
  \includegraphics[height=8in]{../figs/exp_hists}
\label{fig:exp_hists}
\end{figure}

\begin{sidewaysfigure}
\caption{Histograms of 1000 parameter estimates for each of nine
simulation cases with Ricker dynamics. The blue vertical lines are the 
data-generating values.}
  \centering
  \includegraphics{../figs/rick_hists}
\label{fig:rick_hists}
\end{sidewaysfigure}

\begin{sidewaysfigure}
\caption{Histograms of 1000 parameter estimates for each of three
simulation cases with Ricker + immigration dynamics. The blue vertical lines are the 
data-generating values.}
  \centering
  \includegraphics[width=8.5in]{../figs/ricki_hists}
\label{fig:ricki_hists}
\end{sidewaysfigure}

\begin{sidewaysfigure}
\caption{Histograms of 1000 parameter estimates for each of two
simulation cases with geometric-recruitment or Leslie matrix dynamics, each fit with 
exponential and geometric-recruitment models. The blue vertical lines are the 
data-generating values; the data-generating values for $r$ are derived from
the actual dynamic parameters of these models.  No data-generating values
are provided for $\gamma$ or $\omega$ by the Leslie matrix model because
each age class had its own survival and fecundity parameters.}
  \centering
  \includegraphics{../figs/geom_mat_hists}
\label{fig:geom_mat_hists}
\end{sidewaysfigure}

\begin{sidewaysfigure}
\caption{Histograms of 1000 parameter estimates simulated with Gompertz dynamics, 
two generations per year, fit with three different Gompertz models.
The vertical lines are the data-generating values; changing the number of generations
changes the meaning of $r$, so no data-generating values of it are provided for the 
single generation per year cases.}
  \centering
  \includegraphics{../figs/gomp_hists}
\label{fig:gomp_hists}
\end{sidewaysfigure}
%\end{landscape}
